Hierarchical Control for Aircraft Electronic Power Systems

### 2012-12-08 project/report/paper.tex
more results section revisions

\subsection{Example: LL-LMS Preserves Safety in Power Spike}
In this example, we show how the Hierarchical LMS preserves safety when the live workload data demands more power than the historical data predicts. 
At Timestep 1 in the following tables, the live data matches the historical data, and the Optimizing LMS provides safe advice.
However, Timestep 2 has a power spike in Load 3 that is not anticipated in the historical data. 
Relying on the Optimizing-LMS alone at Timestep 2 would result in an unsafe configuration, where 120,000W is draw, while the generator can only produce 100,000W.
Fortunately, the LL-LMS in our Hierarchical controller observes the Load 3 power spike in real-time, and it sheds Load 3 to maintain safety, thus maintaining a total power draw of 80,000W, which is within the generator's 100,000W power cap.

@@

For our first experiment, we simulated the case when there are no power
generator failures in the system using the power usage profile shown in
Figure~\ref{fig:preqnofail}. 
In other words, the real power usage profile (Figure~\ref{fig:preqnofail}) is given to the Optimizing LMS and LL-LMS without any perturbations.
Notice that Bus 1 requests more than 100,000 Watts
between time 30 and 60 and again around time 90. Bus 2, on the other hand,
has a massive power usage between time 50 and 80. We wanted to see how the
Optimizing LMS and the LL-LMS responds to this scenario in isolation. 
%Our results are in Figure~\ref{fig:lshlnofail} and Figure~\ref{fig:lsllnofail}.
Comparing the results, we can see that the LL-LMS will shed a much larger
number of loads (Figure~\ref{fig:lshlnofail}) than the the Optimizing LMS (Figure~\ref{fig:lsllnofail}). 
In particular, the LL-LMS sheds exclusively from loads 6-10 due to the configuration of the priority table.
However, the Optimizing LMS however is much smarter. 
It is able to minimize the number of loads shed by shedding loads much higher up in the priority table.

@@

\subsection{Unexpected Power Spikes}
\label{sec:power-spikes-simulation}
The Optimizing LMS performs a live optimization using historical data for load power requests from previous flights. 
Due to the nature of the optimization problem, it is impossible to program the optimization problem with live data. 
As a result, it is possible for the Optimizing LMS to provide unsafe advice if there is a power spike. 
More specifically, it is possible for the Optimizing LMS to generate a load shedding configuration that could have one of the power generators driving a higher power request than its rating. We want to simulate such a failure case and show that the LL-LMS performs the required adjustment to keep the system in a safe state. 
For this experiment, we use the same historical power request as in Figure~\ref{fig:preqnofail}. 
However, the actual power request for this simulation is shown in Figure~\ref{fig:preqpwrspike}. 
Without the LL-LMS, the Optimizing LMS would use the load shedding configuration seen in Figure~\ref{fig:lshlnofail}. 
Notice that there is a power spike from time 10 to 40 that the historical data does not account for and thus the Optimizing LMS is unaware of. 
As a result, its load shedding configuration would overload the power generator. 
Because we have a LL-LMS, we are able to keep the system in a safe configuration.
Figure~\ref{fig:lsolpwrspike} shows that the LL-LMS will detect that the generators would be overloaded and thus shed some loads during this time interval.

>>>>

\subsection{Example: LL-LMS Preserves Safety in Power Spike}
\label{sec:power-spike-example}
In this example, we show how the Hierarchical LMS preserves safety when the live workload data demands more power than the historical data predicts. 
At Timestep 1 in the following tables, the live data matches the historical data, and the Optimizing LMS provides safe advice.
However, Timestep 2 has a power spike in Load 3 that is not anticipated in the historical data. 
Relying on the Optimizing-LMS alone at Timestep 2 would result in an unsafe configuration, where 120,000W is draw, while the generator can only produce 100,000W.
Fortunately, the LL-LMS in our Hierarchical controller observes the Load 3 power spike in real-time, and it sheds Load 3 to maintain safety, thus maintaining a total power draw of 80,000W, which is within the generator's 100,000W power cap.

@@

We begin by simulating the case when there are no power
generator failures in the system using the power usage profile shown in
Figure~\ref{fig:preqnofail}. 
In other words, the real power usage profile (Figure~\ref{fig:preqnofail}) is given to the Optimizing LMS and LL-LMS without any perturbations.
Notice that Bus 1 requests more than 100,000 Watts
between time 30 and 60 and again around time 90. Bus 2, on the other hand,
has a massive power usage between time 50 and 80. We wanted to see how the
Optimizing LMS and the LL-LMS responds to this scenario in isolation. 
%Our results are in Figure~\ref{fig:lshlnofail} and Figure~\ref{fig:lsllnofail}.
Comparing the results, we can see that the LL-LMS will shed a much larger
number of loads (Figure~\ref{fig:lshlnofail}) than the the Optimizing LMS (Figure~\ref{fig:lsllnofail}). 
In particular, the LL-LMS sheds exclusively from loads 6-10 due to the configuration of the priority table.
However, the Optimizing LMS however is much smarter. 
It is able to minimize the number of loads shed by shedding loads much higher up in the priority table.

@@

\subsection{Unexpected Power Spikes}
\label{sec:power-spikes-simulation}
%The Optimizing LMS performs a live optimization using historical data for load power requests from previous flights. 
%Due to the nature of the optimization problem, it is impossible to program the optimization problem with live data. 
As we showed in Section~\ref{sec:power-spike-example}, it is possible for the Optimizing LMS to provide unsafe advice if there is a power spike. 
More specifically, due to the Optimizing LMS's dependence on historical data, the Optimizing LMS can generate a load shedding configuration that draws more power than the generators can produce. 
We want to simulate such a failure case and show that the LL-LMS performs the required adjustment to keep the system in a safe state. 
For this experiment, the Optimizing LMS is given the historical power loads in Figure~\ref{fig:preqnofail}. 
However, the actual power loads for this simulation is shown in Figure~\ref{fig:preqpwrspike}. 
Without the LL-LMS, the Optimizing LMS would use the load shedding configuration seen in Figure~\ref{fig:lshlnofail}. 
Notice that there is a power spike from time 10 to 40 that the historical data does not account for and thus the Optimizing LMS is unaware of. 
As a result, its load shedding configuration would overload the power generator. 
Because we have a LL-LMS, we are able to keep the system in a safe configuration.
Figure~\ref{fig:lsolpwrspike} shows that the LL-LMS detects that the Optimizing LMS's configuration overloads some generators, and the LL-LMS applies the priority tables to shed some loads during this time interval.
